\cvsection{Experience}
\begin{cventries}
  \cventry
    {Resident Hacker}
    {Moringa School}
    {https://moringaschool.com}
    {Sept. 2015 - Exp. Jan. 2016}
    {
      \begin{cvitems}
         \item {Designed and implemented a problem board using Python Django with which students can remotely assign and ask instructors questions.}
        \item {Taught frontend classes covering HTMl/CSS their frameworks and Javascript frontend frameworks.}
      \end{cvitems}
    }
  \cventry
    {Data Scientist Trainee}
    {Kiva}
    {https://www.kiva.org/}
    {May. 2017 - July. 2017 }
    {
      \begin{cvitems}
        \item { Part of a group that designed and built a machine learning model that could predict time to which loan recipients would recieve their loans and the amount they would recieve using Python.}
      \end{cvitems}
    }
  \cventry
    {Data Scientist Intern}
    {Brave Venture Labs}
    {https://brave.careers}
    {October. 2017 - April. 2018}
    {
      \begin{cvitems}
        \item {Designed a schema and transferred years of accumulated user data stored in Google Drive spreadsheets into a searchable MongoDB database.}
        \item {Performed analyses on job titles and their corresponding companies in an attempt to find job titles that matched the skillset of specific job seekers.}
      \end{cvitems}
    }

  % \cventry
  %   {Freelance Penetration Tester}
  %   {SAMSUNG Electronics}
  %   {S.Korea}
  %   {Sep. 2013, Mar. 2011 - Oct. 2011}
  %   {
  %     \begin{cvitems}
  %       \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
  %       \item {Conducted penetration testing on SAMSUNG Smart TV.}
  %     \end{cvitems}
  %     %\begin{cvsubentries}
  %     %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
  %     %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
  %     %\end{cvsubentries}
  %   }
\end{cventries}
